### 2017-02-27 IROS17/simulation.tex
Added tons of images, still working on writing the algorithm.
added to caption

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{Contour.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:contour}
The contour plot keeps 3 points steady.
}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{Number.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:numberPlot}
Number of moves needed.
}
\end{figure}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{5diagramsplots2.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:4diagramsplots.pdf}
The required number of moves under Alg. \ref{alg:PosControlNRobots}  using wall-friction to rearrange $n$ square-shaped 
robots.  
See hardware implementation and simulation at \cite{Arun2015}.
}
\end{figure}

>>>>

@@

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{5diagramsplots2.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:4diagramsplots.pdf}
The required number of moves under Alg. \ref{alg:PosControlNRobots}  using wall-friction to rearrange $n$ square-shaped 
robots grows quadratically with $n$.  
See hardware implementation and simulation at \cite{Arun2015}.
}
\end{figure}
